Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-02-22 paper/paper.tex
changed headings to be numerical
Update paper.tex

\documentclass[sigconf]{acmart}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

\usepackage{etoolbox} 
\apptocmd{\sloppy}{\hbadness 10000\relax} {}{}

@@

\section*{Introduction}
Introduction

\section*{Methodoloy}
methods

>>>>

\documentclass[sigconf]{acmart}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}} %chktex 1

\usepackage{etoolbox} 
\apptocmd{\sloppy}{\hbadness 10000\relax} {}{} %chktex 1

@@

\section{Introduction}
Introduction
This project will focus on people’s ability to type with distractions such as different types of music playing and then will test their cognitive ability to focus on a hand/eye coordination test in which we will test how well they can match shapes by measuring speed and accuracy. The purpose of the two-part test is to help test if the music is too much of a distraction or will help the people be more efficient at their work. This is important because many people do their homework or jobs while listening to music and should they make a mistake, it could end up costing someone their grade or the mistake at work has a cascading effect to cause more errors in their work. The two-part test will help determine if there is a correlation between the effectiveness of music versus no music on cognitive response time and typing efficiency.

\section{Methodoloy}
methods
